\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-06-30 redaction/revision_JEGeo/referees/answers/Answer_referee1_Lise.tex

\begin{figure}[htbp]
\caption{Accuracy of the estimation of the $\beta$: Comparison}
\label{fig:accuracy_beta}
\begin{center}
\includegraphics[height=4in]{accuracy_beta.pdf}
\end{center}
\end{figure}

Figure \ref{fig:accuracy_beta} In most cases, the log of the ratio is negative, implying a lower interval confidence of the $\beta$ estimate with our methodology. Our method undoubtedly yields more accurate estimations of the share of additive components, whatever the transport mode considered. We have checked that a similar conclusion applies on other years (they are not reported here for sake of brevity but they are available upon request).

\end{itemize}
\end{itemize}

All these elements drive us to maintain our original estimation as benchmark method in the revised version, and we deeply hope to convince you of the relevance of this choice. However, we also want to keep track of this alternative method as further robustness check. Fr this purpose, we have amended the online Appendix with a section devoted to the referee's method.\textbf{ XXX TO BE DONE XXX CHECK THIS SECTION EXISTS IN THE ONLINE APPENDIX XXX}

@@

Not this check is performed both on our main dataset (SITC 5 digit), and also at the HS 10 level, to handle simultaneously the referee's concern about aggregation issues. In the latter case, second-stage estimates are not reported for the sake of space, but do not change anything to previous conclusion - they are very, very similar to their non-IV, least squares counterparts.

\subsubsection{The aggregation problem}

\textit{\textbf{The aggregation problem}: The original annual Census data reports
trade at the origin country-HS10 product-district level of aggregation,
whereas the authors are aggregating up the data even further to the origin
country-HS5 industry-year level. Such an aggregation comes with strong implicit assumptions and sacrifices a lot of useful variation in the data.
The authors are motivating the aggregation by stating that the problem
would become computationally expensive without it. But this reasoning
brings us back to my original point that the authors can use the Hummel's
Methodology to circumvent the computational burden.}

It is true that the original annual Census data reports trade at the origin country-HS 10 product-district level of aggregation. Our initial choice of retaining $s=3$ at the sectoral level, $k=5$ at the product level was driven by the use of Hummel's dataset available over 1974-2004 with $k=5$ the finest degree of aggregation. We yet agree with the referee that jumping from $k=10$ to $k=5$ digits at the product level is detrimental to our ability to exploit useful variation in the data. In line with the referee's comment, we now run the estimation by considering $k$ at the HS10 classification level, not 5. After checking with the US Bureau of Census, data is only available since 1989, now available to 2019. We have hence asked for all available data at the time of revision (1989-2009), and we now present the results considering $s=3$ and $k=10$. This however deprives us from being able to exploit the period 1974-1988 at the aggregation level. \textbf{Que faire pour la periode 1974-1989 XXX TO BE DISCUSSED XXX}. Furthermore, the computational burden mentioned by the referee is not attributable to the product classification level $k=5$ or 10) but rather to the degree of sectoral classification ($s=3$ or 4) as it conditions the number of fixed effects. This explains why we consider the $s=4$ digit- sectoral classification level only for some years. We thank the referee for pointing this ambiguity in our paper, which drove us to rewrite the associated paragraph in the revised version of the paper \textbf{see XXXX TO BE DONE ??? XXX}

% XXX JH: UNLESS I AM MISTAKING, THE SHOPPING LIST BELOW HAS BEEN IMPLEMENTED XXX TO BE CONFIRMED
%\subsubsection{To sum up: What remains to be done}
